Fast and exact visibility on digitized shapes and application to feature-aware normal estimation

### 2025-04-07 DGMM2025/paper.tex
reworked figures and algorithms

\usepackage{changes}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{varwidth}
\usepackage{mathtools}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    % Examples of visibility in 2D
    \begin{figure}
        \centering
        \begin{tikzpicture}
            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.75,2.75);
            \draw[dashed] (0,0) -- (2,1);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p1};
            \filldraw[black] (2,1) circle (0.05) node[anchor=north] {q1};
            \draw [thick] (0,0) -- (0.5,0) -- (1,0) -- (1,0.5) -- (1.5,0.5) -- (1.5,1) -- (2,1);
            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0.5,0.5) -- (0.5,1) -- (1,1) -- (1,1.5) -- (2.5,1.5) -- (2.5,0.5) -- (2,0.5) -- (2,0) -- (1.5,0) -- (1.5,-0.5) -- (-0.5,-0.5);
        \end{tikzpicture}
        \begin{tikzpicture}
            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.25,3.25);
            \draw[red,dashed,thick] (0,0) -- (1.5,1);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p2};
            \filldraw[black] (1.5,1) circle (0.05) node[anchor=north] {q2};
            \draw [thick] (0,0) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (1,1.5) -- (1,1) -- (1.5,1);
            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (0,1.5) -- (0,2) -- (1.5,2) -- (1.5,1.5) -- (2,1.5)  -- (2,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
        \end{tikzpicture}
        \begin{tikzpicture}
            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
            \draw[red,dashed,thick] (0,0) -- (1,0);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p3};
            \filldraw[black] (1,0) circle (0.05) node[anchor=north] {q3};
            \draw [thick] (0,0) -- (0,1) -- (1,1) -- (1,0);
            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,-0.5) -- (-0.5,-0.5) -- (0.5,-0.5) -- (0.5,0.5);
        \end{tikzpicture}
        \begin{tikzpicture}
            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
            \draw[red,dashed,thick] (0,0) -- (1,1);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p4};
            \filldraw[black] (1,1) circle (0.05) node[anchor=north] {q4};
            \draw [thick] (0,0) -- (0,1) -- (1,1);
            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
        \end{tikzpicture}
        \caption{Examples of visibility in 2D, only q1 is visible from p1, q2 is not visible from p2 (gets out of the star), q3 is not visible from p3 (gets out of the star from a 1-d cell), q4 is not visible from p4 (gets out of the star from a 0-d cell).}
        \label{fig:visibility-2d}
    \end{figure}

@@

    % Example of visibility not necessarily connected
    % Path from p to q : r u r u r r r r r u r
    \begin{figure}
        \centering
        \begin{tikzpicture}
            \draw (0,0) -- (1,0) -- (1,1) -- (2,1) -- (2,2) -- (3,2) -- (4,2) -- (5,2) -- (6,2) -- (7,2) -- (7,3);
            \draw [black, dashed] (0,0) -- (7,3);
            \draw [red, dashed] (0,0) -- (7,2);
            \draw [red, dashed] (0,0) -- (6,2);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p};
            \filldraw[gray] (1,0) circle (0.05);
            \filldraw[gray] (1,1) circle (0.05);
            \filldraw[gray] (2,1) circle (0.05);
            \filldraw[gray] (2,2) circle (0.05);
            \filldraw[gray] (3,2) circle (0.05);
            \filldraw[gray] (4,2) circle (0.05);
            \filldraw[gray] (5,2) circle (0.05);
            \filldraw[red] (6,2) circle (0.05);
            \filldraw[red] (7,2) circle (0.05);
            \filldraw[black] (7,3) circle (0.05) node[anchor=west] {q};
            \draw[dashed=gray] (-1,-1) -- (-1,1) -- (0,1) -- (0,2) -- (1,2) -- (1,3) -- (6,3) -- (6,4) -- (8,4) -- (8,1) -- (3,1) -- (3,0) -- (2,0) -- (2,-1) -- (-1,-1);
        \end{tikzpicture}
        \caption{Example of non connex visibility in 2D, q is visible from p while the visibility points are not 26-connected.}
        \label{fig:visibility-2d-not-connected}
    \end{figure}

@@

    \begin{definition}
        An interval $I$ is defined as the pair $[a,b], a \leq b, st. \forall a \leq n \leq b, n \in I$
    \end{definition}

    \begin{definition}
        $\forall A = [a,b], B = [c,d] \in interval, A < B \Leftrightarrow b < c$
    \end{definition}

    \begin{definition}
        An intervals $L$ is an ordered list of intervals ${L_1,\ldots,L_n}$ st. $\forall i \in \mathbb{N}, L_i < L_{i+1}$
    \end{definition}

@@

    \begin{definition}
        All translations $T$ of an interval $A$ on an intervals $L$ is defined as $\{t, st. A+t \subset L\}$
    \end{definition}

    \begin{algorithm}
        \caption{Given a cell complex C and a radius $r$, compute the visibility at every point of C up to distance $r$.}
        \label{alg:visibility}
        \begin{algorithmic}
            \Function{Translation}{I: Interval, L: Intervals}
                \State $[a, b] \gets I$
                \State $Result \gets \emptyset$
                \For{each interval $J$ in L}
                    \State $[c, d] \gets J$
                    \If{$\text{Size}(I) \leq \text{Size}(J)$}
                        \State $Result \gets Result \cap [c-a,d-b]$
                    \EndIf
                \EndFor
                \State \Return Result
            \EndFunction

            \Function{Visibility}{\text{C}: Cell complex, \text{Radius}: integer}
                \State $FigLattices \gets \Call{GetStarFigLattices}{C}$
                \State $Vectors \gets \Call{GetAllPrimalVectors}{Radius}$
                \State $Visibility: \text{vector of boolean} \gets \emptyset$
                \State $minFInterval, maxFInterval \gets \Call{GetMinMaxInterval}{FigLattices}$
                \For{each $V$ in $Vectors$}
                    \State $VLattice \gets \Call{GetLattice}{\text{V}}$
                    \For{every shift $tx, ty$ in $FigLattices$}
                        \State $CurrentIResult \gets [minFInterval, maxFInterval]$
                        \State $StartingPoint \gets \Call{GetStartingPoint}{tx, ty}$
                        \For{each $Lattice$ in $VStarLattice$}
                            \For{each interval $I$ in $Lattice.intervals$}
                                \State $\text{CurrentIResult} \gets \text{CurrentIResult} \cap \Call{Translation}{I, \text{FigLattices}[StartingPoint + Lattice.position])}$
                            \EndFor
                        \EndFor
                        \State \Call{UpdateVisibility}{$Visibility$, $CurrentIResult$}
                    \EndFor
                \EndFor
                \State \Return $Visibility$
            \EndFunction

        \end{algorithmic}
    \end{algorithm}

    \begin{algorithm}
        \caption{Given 2 lists of intervals K and L, find $K \cap L$, the intersection of those 2 lists}
        \label{alg:intersection}
        \begin{algorithmic}
            \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
                \State $R \gets \emptyset$
                \State $k, l \gets 0$
                \While{$k < K.nbIntervals \And l < L.nbIntervals$}
                    \State $[a,b] \gets K[k]$
                    \State $[c,d] \gets L[l]$
                    \State $cMin \gets \max(a, c)$
                    \State $cMax \gets \max(b, d)$
                    \If{$cMax < cMin$}
                        \State $R.append([cMin, cMax])$
                    \EndIf
                    \If{$a \leq d$}
                        \State $k \gets k+1$
                    \EndIf
                    \If{$c \leq b$}
                        \State $l \gets l+1$
                    \EndIf
                \EndWhile
                \State \Return $R$
            \EndFunction
        \end{algorithmic}
    \end{algorithm}

>>>>

\usepackage{changes}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{varwidth}
\usepackage{mathtools}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    % Examples of visibility in 2D
    \begin{figure}
        \centering
        \begin{tabular}{cc|cc}
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.75,2.75);
                \draw[dashed] (0,0) -- (2,1);
                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p1};
                \filldraw[black] (2,1) circle (0.05) node[anchor=north] {q1};
                \draw [thick] (0,0) -- (0.5,0) -- (1,0) -- (1,0.5) -- (1.5,0.5) -- (1.5,1) -- (2,1);
                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0.5,0.5) -- (0.5,1) -- (1,1) -- (1,1.5) -- (2.5,1.5) -- (2.5,0.5) -- (2,0.5) -- (2,0) -- (1.5,0) -- (1.5,-0.5) -- (-0.5,-0.5);
            \end{tikzpicture}&&&
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.25,3.25);
                \draw[red,dashed,thick] (0,0) -- (1.5,1);
                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p2};
                \filldraw[black] (1.5,1) circle (0.05) node[anchor=north] {q2};
                \draw [thick] (0,0) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (1,1.5) -- (1,1) -- (1.5,1);
                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (0,1.5) -- (0,2) -- (1.5,2) -- (1.5,1.5) -- (2,1.5)  -- (2,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
            \end{tikzpicture}\\
            Visible&&&Non Visible\\\\
            \hline\\
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
                \draw[red,dashed,thick] (0,0) -- (1,0);
                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p3};
                \filldraw[black] (1,0) circle (0.05) node[anchor=north] {q3};
                \draw [thick] (0,0) -- (0,1) -- (1,1) -- (1,0);
                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,-0.5) -- (-0.5,-0.5) -- (0.5,-0.5) -- (0.5,0.5);
            \end{tikzpicture}&&&
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
                \draw[red,dashed,thick] (0,0) -- (1,1);
                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p4};
                \filldraw[black] (1,1) circle (0.05) node[anchor=north] {q4};
                \draw [thick] (0,0) -- (0,1) -- (1,1);
                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
            \end{tikzpicture}\\
            Non Visible (from a 1-d cell)&&&Non Visible (from a 0-d cell)
        \end{tabular}
        \caption{Examples of visibility in 2D.}
        \label{fig:visibility-2d}
    \end{figure}

@@

    % Example of visibility not necessarily connected
    % Path from p to q : r u r u r r r r r u r
    \begin{figure}
        \centering
        \begin{tikzpicture}
            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (5.25,3.25);
            \draw[thick] (0,0) -- (0.5,0) -- (0.5,0.5) -- (1,0.5) -- (1,1) -- (3.5,1) -- (3.5,1.5);
            \draw [black, dashed] (0,0) -- (3.5,1.5);
            \draw [red, dashed] (0,0) -- (3.5,1);
            \draw [red, dashed] (0,0) -- (3,1);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p};
            \filldraw[gray] (0.5,0) circle (0.05);
            \filldraw[gray] (0.5,0.5) circle (0.05);
            \filldraw[gray] (1,0.5) circle (0.05);
            \filldraw[gray] (1,1) circle (0.05);
            \filldraw[gray] (1.5,1) circle (0.05);
            \filldraw[gray] (2,1) circle (0.05);
            \filldraw[gray] (2.5,1) circle (0.05);
            \filldraw[red] (3,1) circle (0.05);
            \filldraw[red] (3.5,1) circle (0.05);
            \filldraw[black] (3.5,1.5) circle (0.05) node[anchor=west] {q};
            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0,0.5) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (3,1.5) -- (3,2) -- (4,2) -- (4,0.5) -- (1.5,0.5) -- (1.5,0) -- (1,0) -- (1,-0.5) -- (-0.5,-0.5);
        \end{tikzpicture}
        \caption{Example of non connex visibility in 2D, q is visible from p while the visibility points are not 26-connected.}
        \label{fig:visibility-2d-not-connected}
    \end{figure}

@@

    To improve computation time, we will use lattice sets of integer intervals.

    \begin{definition}
        A sequence of intervals is an ordered list of intervals $L = ([a_i,b_i])_{i=1,\ldots,n}$ such that $b_i + 1 < a_{i+1}$, i.e., disjoint intervals with at least a missing integer.
    \end{definition}

@@

    \begin{definition}
        A translation of a sequence of intervals $L$ is the sequence defined as $L+t \coloneqq \{L_1+t,\ldots,L_n+t\}$
    \end{definition}

    \begin{definition}
        All translations $T$ of an interval or a sequence of intervals $A$ in a sequence of intervals $L$ are defined as $ T \coloneqq t, st. A+t \subset L\}$
    \end{definition}

    We will consider the lattices as a map from points $p \in \R^{d-1}$ to a sequence of intervals, where all coordinates are doubled, so that the represented cell $\forall c \in \R^d$ will have a dimension equal to $\sum_{i=1}^d \left(c[i]\mod2\right)$.

    \begin{figure}
        \centering
        \caption{Representation of a 2d cell complex (here the star of a given curve) as lattices}
        \label{fig:lattice-representation}
        \usetikzlibrary {arrows.meta,decorations.shapes}
        \begin{tabular}{c c}
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.25,-0.25) grid (7.25,7.25);
                \filldraw[black] (1,4) circle (0.05);
                \filldraw[black] (1,5) circle (0.05);
                \filldraw[black] (2,5) circle (0.05);
                \filldraw[black] (3,5) circle (0.05);
                \filldraw[black] (3,4) circle (0.05);
                \filldraw[black] (3,3) circle (0.05);
                \filldraw[black] (3,2) circle (0.05);
                \filldraw[black] (2,2) circle (0.05);
                \filldraw[black] (2,1) circle (0.05);
                \filldraw[black] (1,1) circle (0.05);
                \filldraw[black] (1,0) circle (0.05);
                \filldraw[black] (2,0) circle (0.05);
                \filldraw[black] (3,0) circle (0.05);
                \filldraw[black] (3,1) circle (0.05);
                \filldraw[black] (4,1) circle (0.05);
                \filldraw[black] (5,1) circle (0.05);
                \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=10mm}] {(-1,-1) -- (-1,7)};
                \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
                \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);
            \end{tikzpicture} &
            %      \begin{tikzpicture}
            %     \foreach \y in {1,1.5,...,6} {
            %       \draw[thin, lightgray,xshift=-1cm,yshift=-1cm] (0.75,\y) -- (6.25,\y);
            %     }
            %     \draw[-{Stealth[length=3mm]}=black] (0,0) -- (0,5.5);
            %     \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=10mm}] {(0,0) -- (0,5)};
            %     \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,5)--(3.1,5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,4.5)--(1.1,4.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,4.5)--(3.1,4.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,4)--(1.1,4);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,4)--(3.1,4);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,3.5)--(3.1,3.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,3)--(3.1,3);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,2.5)--(3.1,2.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.9,2)--(3.1,2);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.9,1.5)--(2.1,1.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,1)--(2.1,1);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,1)--(5.1,1);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,0.5)--(1.1,0.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,0.5)--(3.1,0.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,0)--(3.1,0);
            %     \filldraw[white,yshift=-1cm] (0,0) circle (0.01); % readjust the height to match the original path
            % \end{tikzpicture} &
            \begin{tikzpicture}
                \foreach \y in {0,0.5,...,7} {
                    \draw[thin, lightgray,xshift=-1cm,yshift=-1cm] (-0.25,\y) -- (7.25,\y);
                }
                \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=10mm}] {(-1,-1) -- (-1,6.5)};
                \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,5.5)--(3.6,5.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,5)--(3.6,5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,4.5)--(3.6,4.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,4)--(1.6,4);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,4)--(3.6,4);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,3.5)--(1.6,3.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,3.5)--(3.6,3.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,3)--(3.6,3);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2.5)--(3.6,2.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(3.6,2);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,1.5)--(5.6,1.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,1)--(5.6,1);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,0.5)--(5.6,0.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,0)--(3.6,0);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,-0.5)--(3.6,-0.5);
                \filldraw[white,yshift=-1.25cm] (0,0) circle (0.01); % readjust the height to match the original path
            \end{tikzpicture}
        \end{tabular}

    \end{figure}

    \begin{algorithm}
        \caption{Given a cell complex C and a radius $r$, compute the visibility at every point of C up to distance $r$. We assume z being the lattice main axis, x and y being the auxiliary axises}
        \label{alg:visibility}
        \begin{algorithmic}
            \Function{Visibility}{\text{C}: Cell complex, \text{r}: Integer}
                \State $\Omega \gets \Call{Star}{C}$ \Comment{Lattices of the star of the studied cell complex}
                \State $Vectors \gets \Call{GetAllPrimalVectors}{r}$
                \State $V: \text{vector of boolean} \gets [0, \ldots, 0]$ \Comment{length $Size(Vectors) * PointelsAmount$}
                \State $low, high \gets \Call{BoundingBoxZ}{\Omega}$
                \ForAll{$v$ in $Vectors$}
                    \State $VStar \gets \Call{Star}{\text{v}}$
                    \ForAll{shift $tx, ty$ in $\Omega$}
                        \State $R \gets [low, high]$
                        \State $S: \R^3 \gets [2tx, 2ty,0]$
                        \ForAll{lattice $L$ in $VStar$}
                            \State $\text{R} \gets \text{R} \cap \Call{Translations}{L.intervals,\Omega[S + L.position]}$
                        \EndFor
                        \State \Call{UpdateVisibility}{$V$, $R$}
                    \EndFor
                \EndFor
                \State \Return $V$
            \EndFunction
        \end{algorithmic}
    \end{algorithm}

    \begin{algorithm}
        \caption{Given 2 lists of intervals $K$ and $L$, find $K \cap L$, the intersection of those 2 lists}
        \label{alg:intersection}
        \begin{algorithmic}
            \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
                \State $R \gets \emptyset$
                \State $k, l \gets 0$
                \While{$k < K.nbIntervals \And l < L.nbIntervals$}
                    \State $[a,b] \gets K[k]$
                    \State $[c,d] \gets L[l]$
                    \State $e \gets \max(a, c)$
                    \State $f \gets \min(b, d)$
                    \If{$e < f$}
                        \State $R.append([e, f])$
                    \EndIf
                    \If{$b \leq d$}
                        \State $k \gets k+1$
                    \EndIf
                    \If{$d \leq b$}
                        \State $l \gets l+1$
                    \EndIf
                \EndWhile
                \State \Return $R$
            \EndFunction
        \end{algorithmic}
    \end{algorithm}
